Closed-loop Neuromorphic Benchmarks

### 2015-10-01 paper/paper.tex
Added conclusion about adaptive control

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is a
    closed-loop task; that is, a task where the output from the neuromorphic
    hardware affects some environment, which then in turn affects the
    hardware's future input.  However, closed-loop situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for generating closed-loop benchmarks that makes use
    of a hybrid of real physical embodiment and a type of ``minimal'' simulation.
    Minimal simulation has been shown to lead to robust real-world performance,
    while still maintaining the practical advantages of simulation, such as
    making it easy for the same benchmark to be used by many researchers.
    This method is flexible enough to allow researchers to explicitly
    modify the benchmarks to identify specific task domains where particular
    hardware excels.  To demonstrate the method, we present a set of novel benchmarks
    that focus on motor control for an arbitrary system with
    unknown external forces.

@@

@@

>>>>

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is a
    closed-loop task; that is, a task where the output from the neuromorphic
    hardware affects some environment, which then in turn affects the
    hardware's future input.  However, closed-loop situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for generating closed-loop benchmarks that makes use
    of a hybrid of real physical embodiment and a type of ``minimal'' simulation.
    Minimal simulation has been shown to lead to robust real-world performance,
    while still maintaining the practical advantages of simulation, such as
    making it easy for the same benchmark to be used by many researchers.
    This method is flexible enough to allow researchers to explicitly
    modify the benchmarks to identify specific task domains where particular
    hardware excels.  To demonstrate the method, we present a set of novel benchmarks
    that focus on motor control for an arbitrary system with
    unknown external forces.  Using these benchmarks, we show that an error-driven
    learning rule can consistently improve motor control performance across
    a randomly generated family of closed-loop simulations, even when there are
    up to 15 interacting joints to be controlled.

@@

While the primary purpose of this paper is in decribing the benchmarking
methodology, it is also worth noting that these benchmarks indicate
that the neuromorphic learning rule under investigation here is extremely robost.  As
shown in \ref{fig:analysis_neurons_cpu}, even just 500 neurons can consistently
adapt to control a \emph{randomly generated} 15-joint body simulation, and
deal with larger delays and noise than were seen in the example 1-joint
physical embodiment.  Since this learning system is robust across such a
wide range of conditions, and since it is efficiently implementable in a
wide variety of neuromorohic hardware, we feel it is worth further study.  This must include 
both a wider variety of minimal simulation benchmarks and also a few more 
traditional benchmarks.  These traditional
benchmarks would be particular real physical systems (specific robot arms,
for example), but testing on those would only reveal performance on those
particular arms.  As we argued here, benchmarking against a wide variety of 
randomly generated minimal simulation systems is needed to demonstrate the
space of potential situations in which neuromorphic adaptive control performs well.

@@

Finally, we note that the benchmarking results show that this learning rule
can consistently improve control performance across a wide variety of randomly
generated situations, and is suitable for implementation on a wide variety
of neuromorphic hardware.  Given this promising result, we will be further
evaluating it on specific physical embodiments, and comparing it to more
complex variants of PID control.
